---
title: "Stock_price_prediction"
author: "Anushka Kapoor"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
#REQUIRED LIBRARIES
library(rvest)
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
#install.packages(c("zoo", "ggplot2"))
library(zoo)
```


Reading the data from the URL and creating a data frame out of it named as sp500.
Columns-
Ticker: Symbol of the stock
Name: Name of the stock
Sector: Sector to which the stock belongs
Industry: Industry to which the stock belongs
HQ_Location: Headquarter location of the company of the stock

returns Data frame:
Open: Opening price of stock
Low: Lowest price of stock
Close: Closing price of stock
High: Highest price of stock
Movement: Net movement of the stock for a day

Loading the Data frames created.
```{r}
load("~/Desktop/MSBA Class'24/Machinelearning/MachineLearning/sp500.RData")
load("~/Desktop/MSBA Class'24/Machinelearning/MachineLearning/returns.RData")
load("~/Desktop/MSBA Class'24/Machinelearning/MachineLearning/returns_long.RData")
load("~/Desktop/MSBA Class'24/Machinelearning/MachineLearning/returns_sp500.RData")
```

```{r}
#choosing "Microsoft" as the stock for which we want to see the plot.We can try other ticker values to see plots for other stocks (AAPL, GOOGL, AMZN, BLK etc)
ticker <- "MSFT"

charting_data <- returns_sp500 %>% filter(Ticker == ticker, Date >= "2023-06-24")
plotting_data <- returns_long %>% filter(Ticker == ticker, Date >= "2023-09-02")
```

Stock Price trend for Microsoft.
```{r}
candlestick <- ggplot(plotting_data) +
  geom_boxplot(aes(x = as.character(Date), y = Value, color = Movement), width = 0.2) +
  scale_color_manual(values = c(Up = "green", Down = "red")) +
  xlab("Date") + 
  ylab("Stock Price") +
  labs(
    title = paste0(plotting_data$Name[1], " (", ticker, ")"),
    subtitle = plotting_data$Sector[1],
    caption = "Source: Yahoo! Finance"
    )+
  scale_y_continuous(labels = scales::dollar)+
  theme(
   plot.background = element_rect(fill = "#17202A"),
    panel.background = element_rect(fill = "#17202A"),
    axis.text.x = element_text(color = "#ffffff", angle = 45, hjust = 1, vjust = 1),
    axis.text.y = element_text(color = "#ffffff"),
    axis.title.y = element_text(color = "#ffffff"),
    axis.title.x = element_text(color = "#ffffff"),
    plot.title = element_text(color = "#ffffff"),
    plot.subtitle = element_text(color = "#ffffff"),
    plot.caption = element_text(color = "#ffffff", face = "italic", size = 6),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "#273746"),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    legend.position = "none",
    )
candlestick
```

Moving average for 10, 20 and 50 days
```{r}
# Calculate moving averages using rollapply
charting_data$MA_10 <- rollapply(charting_data$Close, width = 10, FUN = mean, align = "right", fill = NA)
charting_data$MA_20 <- rollapply(charting_data$Close, width = 20, FUN = mean, align = "right", fill = NA)
charting_data$MA_50 <- rollapply(charting_data$Close, width = 50, FUN = mean, align = "right", fill = NA)

# Plot the data with moving averages
ggplot(charting_data, aes(x = Date, y = Close)) +
  geom_line(color = "blue", size = 1) +  # Closing price line
  geom_line(aes(y = MA_10), color = "green", size = 1, linetype = "dashed") +  # 10-day moving average
  geom_line(aes(y = MA_20), color = "orange", size = 1, linetype = "dashed") +  # 20-day moving average
  geom_line(aes(y = MA_50), color = "red", size = 1, linetype = "dashed") +  # 50-day moving average
  labs(
    title = "Stock Price with Moving Averages",
    x = "Date",
    y = "Stock Price"
  ) +
  theme_minimal()
```

Comparing the stock price trend for Apple, Microsoft and Google.

```{r}
# Filter data for the specified tickers
selected_tickers <- c("AAPL", "MSFT", "GOOGL")
filtered_data <- returns_sp500[returns_sp500$Ticker %in% selected_tickers, ]

# Plot the Adj_Close prices for the selected tickers
ggplot(filtered_data, aes(x = Date, y = Close, color = Ticker)) +
  geom_line() +
  labs(
    title = "Comparison of Close Prices",
    x = "Date",
    y = "Close Price",
    color = "Ticker"
  ) +
  theme_minimal()
```

```{r}
# Plotting relationship between Open and Close
ggplot(returns_sp500, aes(x = Open, y = Close)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Open vs Close", x = "Open Price", y = "Close Price")+
  theme_minimal()+theme(panel.grid = element_blank())

# Plotting relationship between High and Close
ggplot(returns_sp500, aes(x = High, y = Close)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "High vs Close", x = "High Price", y = "Close Price")+
  theme_minimal()+theme(panel.grid = element_blank())

# Plotting relationship between Volume and Close
ggplot(returns_sp500, aes(x = Volume, y = Close)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Volume vs Close", x = "Volume", y = "Close Price")+
  theme_minimal()+theme(panel.grid = element_blank())

# Plotting relationship between Low and Close
ggplot(returns_sp500, aes(x = Low, y = Close)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Low vs Close", x = "Low", y = "Close Price")+
  theme_minimal()+theme(panel.grid = element_blank())
```

